My title

### 2024-11-04 paper/paper.qmd
updated paper

```{r}
#| label: fig-transparency
#| fig-cap: Distribution of Transparency Scores
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-sample
#| fig-cap: Distribution of Sample Sizes
#| echo: false
#| message: false
#| warning: false

>>>>

```{r}
#| label: fig-transparency
#| fig-cap: Distribution of Poll Transparency Scores
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-sample
#| fig-cap: Distribution of Poll Sample Sizes
#| echo: false
#| message: false
#| warning: false
